The Strong Gravitational Lens Finding Challenge

### 2017-03-06 paper.tex
Edit.

\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

\title[SL Challenge]{Strong Gravitational  Lensing Finding Challenge}

\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1}$\thanks{E-mail: robertbenton.metcalf@unibo.it} R\'emi Cabanac,$^2$ 
A. N. Other,$^3$ \\
% List of institutions
$^{1}$Department of Physics and Astronomy, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
$^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
}

@@

\subsection{GAHEC IRAP}

@@

\red{Reference to figure \ref{fig:Cabanac}?}
\section{results}

@@

>>>>

\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{hyperref}

@@

\title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}

\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} M. Meneghetti,$^4$ R\'emi Cabanac,$^2$ Emmanuel Bertin,$^3$ 
and  \\
% List of institutions
$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
$^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
$^{3}$ Sorbonne Universités, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014, Paris \\
$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
}

@@

\subsection{GAHEC IRAP (Remi Cabanac)}

@@

\red{Reference to figure \ref{fig:Cabanac}?}

\subsection{AstrOmatic (Emmanuel Bertin)}

The lens detector is based on a convolutional neural network (CNN), trained with the provided training datasets. The CNN is implemented in Python, using the TensorFlow framework\footnote{http://www.tensorflow.org/}. Both ground multichannel and space monochannel image classifiers have the exact same CNN architecture.

The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer. The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation. Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.

Prior to entering the first convolutional layer, input image data are rescaled and dynamic-range compressed with function $f(x) =
\mathrm{arcsinh} (10^{11} x)$, and bad pixels are simply set to 0.
Data augmentation is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range. Additionally, a small rotation with random angle $\theta$ is applied, involving bicubic image resampling. $\theta$ follows a Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma_{\theta}=5^{\circ}$. No attempt was made to generate and randomize bad pixel masks in the data augmentation process.

The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$. The network is trained on a Titan-X ``Pascal'' nVidia GPU using the Adam gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch. Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.

\section{results}

@@

EB thanks Raphael Gavazzi for proposing him to participate to the challenge.
